%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Vaibhav Raj Harsh} \\ \vspace{5pt}

    \small
    \faEnvelope \hspace{2pt}
    \href{mailto:vaibhav.vrh@gmail.com}{\texttt{vaibhav.vrh@gmail.com}}
    \hspace{6pt} $|$ \hspace{6pt}
    \faGithub \hspace{2pt}
    \href{https://github.com/vaibhavrajharsh}{\texttt{github.com/vaibhavrajharsh}}
    \hspace{6pt} $|$ \hspace{6pt}
    \faLinkedin \hspace{2pt}
    \href{https://www.linkedin.com/in/vaibhavrajharsh}{\texttt{linkedin.com/in/vaibhavrajharsh}}

    \\[2pt]

    \faPhone* \hspace{2pt} \texttt{+91 9060917098}
    \hspace{10pt} $|$ \hspace{10pt}
    \faMapMarker \hspace{2pt} Patna, Bihar, India
\end{center}

\vspace{4pt}

%-----------SUMMARY-----------
\section{SUMMARY}

\small
Full Stack Developer with hands-on experience building scalable web applications using React.js, Next.js, Node.js, Express.js, MongoDB, and PostgreSQL. Experienced in designing REST APIs, implementing secure authentication, server-side rendering, SEO optimization, and deploying production-ready applications. Passionate about software engineering, scalable system design, and open-source contributions.

\vspace{4pt}


%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

     \resumeSubheading
  {FinnovaCA}{April 2026 - June 2026}
  {Software Engineer}{Remote}
  \resumeItemListStart
    \resumeItem{Designed, developed, tested, and deployed the complete \textbf{Finnova CA} web platform using \textbf{Next.js, Express.js, MongoDB, and Tailwind CSS}, delivering a production-ready solution for financial advisory services.}

\resumeItem{Designed scalable \textbf{frontend architecture, backend services, REST APIs, and database schema}, ensuring maintainability, performance, and responsive user experience across devices.}

\resumeItem{Implemented \textbf{SEO optimization}, server-side rendering (SSR), metadata optimization, sitemap generation, and Core Web Vitals improvements to increase search engine visibility and application performance.}

\resumeItem{Managed end-to-end deployment, hosting, domain configuration, and collaborated directly with the client throughout requirement gathering, development, testing, and project delivery.}

  \resumeItemListEnd
  
    \resumeSubheading
  {Invigo Infotech}{June 2025}
  {Full Stack Developer Intern (MERN Stack)}{Purnea, Bihar}
  \resumeItemListStart
    \resumeItem{Designed and developed scalable backend architecture and REST APIs for a Music Player Application using Express.js and MongoDB.}

\resumeItem{Implemented secure JWT authentication, Role-Based Access Control (RBAC), bcrypt password hashing, Multer file uploads, ImageKit integration, and cookie-based session management.}

\resumeItem{Built a Banking Ledger System backend implementing idempotency keys, ledger entries for every transaction, and MongoDB transaction sessions to ensure consistency and reliability.}

\resumeItem{Developed secure transaction APIs with automated email notifications, balance validation, account status verification, and JWT token blacklisting for enhanced application security.}

  \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
     \resumeProjectHeading
    {\textbf{CiviSence - Civic Issue Management System} $|$ \emph{ReactJS, REST API}}{Feb 2026 -- Present}
    \resumeItemListStart
        \resumeItem{Developed a full-stack civic issue management platform currently serving \textbf{100+ users}, enabling issue reporting with image uploads, geolocation, and real-time status tracking.}

\resumeItem{Built secure REST APIs using Express.js and MongoDB with JWT authentication, Role-Based Access Control (RBAC), image uploads, and complete issue lifecycle management.}

\resumeItem{Designed independent portals for Citizens, Organizations, Admins, and Staff supporting issue assignment, verification, progress tracking, resolution workflows, and feedback collection.}

\resumeItem{Integrated push notifications, cloud storage, responsive dashboards, interactive analytics, and SEO optimization while following scalable MERN architecture and modern software engineering practices.}

    \resumeItemListEnd    
    \resumeProjectHeading
{\textbf{AI Resume Analyzer} $|$ \emph{React.js, Express.js, MongoDB, Gemini API}}{May 2026}
\resumeItemListStart
    \resumeItem{Developed a full-stack AI-powered resume analysis platform that generates ATS scores, keyword optimization, resume parsing, and personalized improvement suggestions.}

\resumeItem{Integrated Google Gemini API to provide intelligent resume feedback, skill gap analysis, role-specific recommendations, and AI-generated career insights.}

\resumeItem{Built secure authentication, PDF resume upload, report history, dashboard, and REST APIs using Express.js, MongoDB, and JWT authentication.}

\resumeItem{Designed a responsive React.js frontend with real-time analysis, downloadable reports, and optimized user experience across devices.}
\resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shri Phanishwar Nath Renu Engineering College Araria}{Aug. 2023 -- Present}
      {Bachelor of Technology in Computer Science and Engineering | CGPA 
      : 7.51}{Araria, India}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Machine Learning}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
   \textbf{Languages:} JavaScript, TypeScript, C++, Python, SQL

\textbf{Frontend:} React.js, Next.js, React Native, HTML5, CSS3, Tailwind CSS

\textbf{Backend:} Node.js, Express.js, REST APIs, JWT Authentication, RBAC

\textbf{Database:} MongoDB, MySQL, PostgreSQL

\textbf{Cloud \& DevOps:} Firebase, ImageKit, Git, GitHub, Vercel, Render

\textbf{Tools:} Postman, Figma, VS Code, Notion
    }}
 \end{itemize}

\section {OPEN SOURCE EXPERIENCE}
  \resumeSubHeadingListStart
\resumeSubheading
{Open Source Contributor}{2024 -- Present}
{GirlScript Summer of Code, Social Winter of Code, HacktoberFest}{Remote}
\resumeItemListStart
\resumeItem{Contributed \textbf{100+ merged pull requests} across GirlScript Summer of Code (GSSoC), Social Winter of Code (SWOC), and HacktoberFest.}

\resumeItem{Collaborated with \textbf{50+ developers} through GitHub issues, pull requests, and code reviews while following industry-standard Git workflows.}

\resumeItem{Implemented features, bug fixes, UI enhancements, and documentation improvements across multiple React and JavaScript open-source projects.}

\resumeItem{Successfully completed HacktoberFest'24 and actively contributed as both an open-source contributor and project maintainer during community programs.}

\resumeItemListEnd

\section{CERTIFICATIONS}

\resumeItemListStart
\resumeItem{Postman API Fundamentals Student Expert}
\resumeItem{Google Cloud Arcade Facilitator Program}
\resumeItem{HacktoberFest 2024}
\resumeItemListEnd


%-------------------------------------------
\end{document}
